---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SS4864Aproject)
```
```{r}
CTSIB <- read.csv("ctsib.csv")# download the CTSIB data
summary(CTSIB)# get the summary of subject, sex, age, height, weight, surface, vision, CTSIB
```
```{r}
#here what we are interested in are surface, vision, and CTSIB, so we edit the data.
ctsib <- CTSIB %>%
  mutate(stable = 1 * (CTSIB == 1))
summary(ctsib)
```
```{r}
#the value of surface and vision are all characters. When we change them to the numeric value, it can have a lot of non-convergence situations.
#in fact,  when we divide 480 numbers into 40 random effects, there will be 12 numbers a group which is small. When we randomly select numbers again later, there will be many repetitions with the same number, which may cause non-convergence.
#hence, we choose to use cross table that the stable has different values with 0 and 1.
ctsib <- tibble(
    Surface = as.factor(ctsib$Surface),
    Vision = as.factor(ctsib$Vision),
    stable = as.factor(ctsib$stable)
  )
table(ctsib)
```
```{r message=FALSE, warning=FALSE}
GLMM("ctsib.csv")# use GLMM function
```
The first row is the intercept. It means that when surface is foam and vision is close, for the effect to the stable: 
  the coefficient is -10.9806411;
  the standard error is 6.399592;
  the confidence interval is (-23.5238407,1.562558);
  the Z-value is -5.760559 and the P-value is 8.383585e-09.
The intercept is significant to the stable.

The second row is the surface norm. It means that when surface is norm and vision is close, for the effect to the stable:
  the coefficient is 7.8424778;
  the standard error is 4.309210;
  the confidence interval is (-0.6035729,16.288528);
  the Z-value is 6.027186 and the P-value is 1.668387e-09.
The surface norm is significant to the stable.

The third row is the vision dome. It means that when surface is foam and vision is dome, for the effect to the stable:
  the coefficient is 0.6903588;
  the standard error is 0.920573;
  the confidence interval is (-1.1139642,2.494682);
  the Z-value is 1.291894 and the P-value is 1.963939e-01.
The vision dome is not significant to the stable.

The fourth row is the vision open. It means that when surface is foam and vision is open, for the effect to the stable: 
  the coefficient is 6.5929871;
  the standard error is 3.778452;
  the confidence interval is (-0.8127790,13.998753);
  the Z-value is 5.449193 and the P-value is 5.059891e-08.
The vision open is significant to the stable.

The 40 random effect ~ N(0,sigma^2). They have the estimated mean for the sigma^2 is 11.19721 with standard error 58.07444. The confidence interval is (-102.6287,125.0231).
The fluctuation of sigma^2 is relatively stable.
